---
title: "Iris Cluster Application"
author: "Thiago Almeida"
date: "31 de julho de 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This is a documentation of the Iris Cluster application. The obective of this application is to show the diference of variables using the kmeans function, which perform k-means clustering on a data matrix.

Example:

`kmeans(x, centers)`

## Dataset

The dataset used in this appliction is a derivation of the iris default dataset.

```{r iris}
  head(iris)
  
```


With a additional columns called SpeciesChar, as shown below.

```{r load}
  dataset <- iris
  dataset$SpeciesChar <- ifelse(dataset$Species == 'setosa', 'S', ifelse(dataset$Species == 'versicolor', 'V', 'I'))
  
```

## Interface

The application has 3 inputs:

* Cluster count: It is the number o cluster used in the kmeans function
* Show Sepal Chart: It is the char Sepal.Width x Sepal.Lenght
* Show Petal Chart: It is the char Petal.Width x Petal.Lenght

## Sample Output 

With cluster count iqual to 3

```{r sample, echo = FALSE}
  # Combine the Sepal variables into a new data frame
  selectedData1 <- dataset[, c('Sepal.Length', 'Sepal.Width')]

  # Combine the Petal variables into a new data frame
  selectedData2 <- dataset[, c('Petal.Length', 'Petal.Width')]

  # Execute the kmeans function with Sepal values
  clusters1 <- kmeans(selectedData1, 3)
  
  # Execute the kmeans function with Petal values
  clusters2 <- kmeans(selectedData2, 3)
  
  # Sepal Chart
    plot(selectedData1,
         col = clusters1$cluster,
         pch = as.character(dataset$SpeciesChar), 
         cex = 2)
    points(clusters1$centers, pch = 4, cex = 4, lwd = 4)

  
  # Petal Chart
    plot(selectedData2,
         col = clusters2$cluster,
         pch = as.character(dataset$SpeciesChar), 
         cex = 2)
    points(clusters2$centers, pch = 4, cex = 4, lwd = 4)
  
```

## References

https://www.rdocumentation.org/packages/openintro/versions/1.7.1/topics/iris
